Cognitive Context: Impact on the Perception of a Robot

### 2015-10-29 main.tex
Various APA style changes

\subsection{Role of context in human-robot interaction}

@@

\subsection*{Measuring anthropomorphism}

@@

\section{Experimental Design}

@@

\section{Experiment}

@@

We ran the study with 56 participants (mean age: 20.9, $SD=3.9$, 31 females and
25 males).  The participants were recruited amongst students of our university.
To avoid students with a high familiarity with robots and artificial intelligent
systems, Computer Science and Electronics curriculum were excluded. This was
\textit{a posteriori} comforted by the questionnaire responses: no participants
reported itself as being very familiar with robots, 8 reported some familiarity
and 7 out of 56 owned a domestic robot (vacuum cleaner).

As stated previously, the study follows a 2$\times$2 design
(table~\ref{table:design}): the \emph{deep} \vs \emph{shallow cognitive context}
condition was between-subjects (30 participants performed the \emph{deep cognitive}
tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
\vs \emph{human} condition was within-subject (the order of stimuli presentation
was counter-balanced over the 56 participants). The study lasted in average 15
minutes per participant.

@@

\paragraph{Familiarization and pre-questionnaire}

@@

\paragraph{Stimuli screening}

@@

\paragraph{Post-questionnaire and conclusion}

Finally, the participants were asked to fill a post-questionnaire.

Before leaving, possible questions on the purpose of the study were
answered and each participant was given a reward equivalent to EUR 10.

\subsection{Data Collection}

\subsubsection{Gaze variables}

As seen in figure~\ref{fig:aoi}, we defined 10 areas of interest (AOIs): one on
the head of the agent (robot or human), two on the arms (left and right), two on
the hands, two on the legs and one on the torso. Besides, we defined one area of
interest per toy or speaker (depending on the stimulus).

@@

    \caption{Areas of interest used for the gaze analysis}
    \label{fig:aoi}
\end{figure}

We recorded the fixations on each of these 10 zones and normalized by different
total video duration and surface of AOIs between the robot and human conditions.
We finally analyzed their distribution, producing what we call \emph{gaze
patterns}.

To compare gazing behaviours across the robot and human conditions, we then
computed a \emph{difference in gaze patterns} over the $N(=10)$ AOIs:

{\large
\[
    \delta_{\mathcal{H}, \mathcal{R}}^{\text{gaze}} =
    \frac{\sum\limits_{{\text{{\sc aoi}s}}}\left |
    \frac{\text{Time}_{\text{Human}}^{\text{\sc
aoi}}}{\text{Area}_{\text{Human}}^{\text{\sc aoi}}} -
\frac{\text{Time}_{\text{Robot}}^{\text{\sc
aoi}}}{\text{Area}_{\text{Robot}}^{\text{\sc aoi}}} \right |}{N}
\]
}

@@

\subsubsection{Questionnaires processing}
\label{questionnaires_processing}

@@

\section{Results}

@@

\subsection{Manipulation check}

@@

Participants were asked in the post-questionnaire whether the video presented a
\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
task). As can be seen in figure 2, we got a significant correlation in this
manipulation check ($F[1,54] = 29.0, p < .001$) which validates our manipulation
and supports \h{1}: the participants that were shown the \emph{shallow cognitive
context} videos identified the task as more robot-like and participants watching
\emph{deep cognitive context} videos perceived the tasks as more human-like.

\subsection{Impact of the tendency to anthropomorphize on human
gazing behaviours}

We found a significant correlation between
$\delta_{\mathcal{H},\mathcal{R}}^{\text{gaze}}$ and
the \anti{}. As seen in figure~\ref{h2}, there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient = -0.43,
$p < .001$). The higher the (initial) tendency to anthropomorphize, the smaller
the difference in gazing behaviours between the robot and human conditions. This
supports hypothesis \h{2}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{H2}\label{GazeDifference-vs-ICA}
    \caption{Difference in gaze patterns $\delta_{\mathcal{H},
    \mathcal{R}}^{\text{gaze}}$ \vs \anti{}}
    \label{h2}
\end{figure}

\subsection{Gaze behaviours in shallow \vs deep cognitive contexts}

We consider the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf hands}, {\sf
torso} and {\sf legs} (the left and right arms, hands and legs are grouped
together). Based on ANOVA results for the robot in both the shallow and deep
cognitive context conditions, the fixations on the head in the deep condition
were found to be significantly higher than that in the shallow condition
($F[1,54] = 4.2, p < .05$). For all other AOIs groups, the fixations across
shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
distribution of proportion of time spent gazing on the 5 AOI groups for the two
conditions.

@@

\subsection{Correlation between cognitive context and changes in anthropomorphic
attributions}

Running an ANOVA against the change of anthropomorphic attributions
(\deltaant) over the duration of the experiment in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F[1,54] = 6.54, p < .05$,
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with a deeper cognitive context report
a significantly higher tendency to anthropomorphize robots \emph{in general} (as
the questionnaire on anthropomorphic attributions explicitly referred to
\emph{robots in general}).

@@

\section{Discussion and Conclusion}

\subsection{Discussion of the results}

@@

\subsection{Design of the stimuli and applicability of the method to real world
scenarios}
\label{stimuli_design}

>>>>

\subsection{Role of Context in Human-Robot Interaction}

@@

\subsection*{Measuring Anthropomorphism}

@@

\pagebreak
\section{Experimental Design}

@@

\pagebreak
\section{Method}

@@

We ran the study with 56 participants ($M = 20.9$ years old, $SD = 3.9$, 31 females and
25 males).  The participants were recruited amongst students of our university.
To avoid students with a high familiarity with robots and artificial intelligent
systems, Computer Science and Electronics curriculum were excluded. This was
\textit{a posteriori} comforted by the questionnaire responses: no participants
reported itself as being very familiar with robots, 8 reported some familiarity
and 7 out of 56 owned a domestic robot (vacuum cleaner).

As stated previously, the study follows a 2$\times$2 design
(table~\ref{table:design}): the \emph{deep} \vs \emph{shallow cognitive context}
condition was between-subjects (30 participants performed the \emph{deep cognitive}
tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
\vs \emph{human} condition was within-subject (the order of stimuli presentation
was counter-balanced over the participants). The study lasted in average 15
minutes per participant.

@@

\subsubsection{Familiarization and Pre-questionnaire}

@@

\subsubsection{Stimuli Screening}

@@

\subsubsection{Post-questionnaire and Conclusion}

Finally, the participants were asked to fill a post-questionnaire.
Before leaving, possible questions on the purpose of the study were
answered and each participant was given a reward equivalent to EUR 10.

\subsection{Measures}

\subsubsection{Gaze Variables}

As seen in figure~\ref{fig:aoi}, we defined 10 Areas of Interest (AOIs): one on
the head of the agent (robot or human), two on the arms (left and right), two on
the hands, two on the legs and one on the torso. Besides, we defined one area of
interest per toy or speaker (depending on the stimulus).

@@

    \caption{Areas of Interest (AOIs) used for the gaze analysis}
    \label{fig:aoi}
\end{figure}

We recorded the fixations on each of these zones and normalized them by
the full duration of the video stimulis and the surface of AOIs between the robot
and human conditions. We finally analyzed their distribution, producing what we call \emph{gaze
patterns}.

To compare gazing behaviours across the robot and human conditions, we besides
computed a \emph{gaze distribution difference} over the 10 AOIs ($N=10$):

{\Large
\[
    \delta_{\mathcal{H}, \mathcal{R}}^{\text{gaze}} =
    \frac{\sum\limits_{{\text{{\sc aoi}s}}}\left |
    \frac{\text{Time}_{\text{Human}}^{\text{\sc
aoi}}}{\text{Area}_{\text{Human}}^{\text{\sc aoi}}} -
\frac{\text{Time}_{\text{Robot}}^{\text{\sc
aoi}}}{\text{Area}_{\text{Robot}}^{\text{\sc aoi}}} \right |}{N}
\]
}

@@

\subsubsection{Questionnaires Processing}
\label{questionnaires_processing}

@@

\pagebreak
\section{Results}

@@

\subsection{Manipulation Check}

@@

Participants were asked in the post-questionnaire whether the video presented a
\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
task). As can be seen in figure 2, we got a significant correlation in this
manipulation check ($F(1,54) = 29.0, p < .001$) which validates our manipulation
and supports \h{1}: the participants that were shown the \emph{shallow cognitive
context} videos identified the task as more robot-like and participants watching
\emph{deep cognitive context} videos perceived the tasks as more human-like.

\subsection{Impact of the Tendency to Anthropomorphize on Human
Gazing Behaviours}

We found a significant correlation between
$\delta_{\mathcal{H},\mathcal{R}}^{\text{gaze}}$ and
the \anti{}. As seen in figure~\ref{h2}, there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient $r(54) = -0.43,
p < .001$). The higher the (initial) tendency to anthropomorphize, the smaller
the difference in gazing behaviours between the robot and human conditions. This
supports hypothesis \h{2}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{H2}\label{GazeDifference-vs-ICA}
    \caption{Gaze distribution difference $\delta_{\mathcal{H},
    \mathcal{R}}^{\text{gaze}}$ \vs initial tendency to anthropomorphize \anti{}}
    \label{h2}
\end{figure}

\subsection{Gaze Behaviours in Shallow \vs Deep Cognitive Contexts}

We consider the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf hands}, {\sf
torso} and {\sf legs} (the left and right arms, hands and legs are grouped
together). Based on ANOVA results for the robot in both the shallow and deep
cognitive context conditions, the fixations on the head in the deep condition
were found to be significantly higher than that in the shallow condition
($F(1,54) = 4.2, p < .05$\fixme{put the exact p value here}). For all other AOIs groups, the fixations across
shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
distribution of proportion of time spent gazing on the 5 AOI groups for the two
conditions.

@@

\subsection{Correlation Between Cognitive Context and Changes in Anthropomorphic
Attributions}

Running an ANOVA against the change of anthropomorphic attributions
(\deltaant) over the duration of the experiment in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F(1,54) = 6.54, p <
.05$\fixme{put the exact p value here},
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with a deeper cognitive context report
a significantly higher tendency to anthropomorphize robots \emph{in general} (as
the questionnaire on anthropomorphic attributions explicitly referred to
\emph{robots in general}).

@@

\pagebreak
\section{Discussion and Conclusion}

\subsection{Discussion of the Results}

@@

\subsection{Design of the Stimuli and Applicability of the Method to Real World
Scenarios}
\label{stimuli_design}
